\documentclass[11pt]{article}
\input{./probpreamble.tex}

\begin{document}

\mytitlecompact{Week 13 Problems}
\nolinebreak \begin{center}  Alex Skeldon \end{center}

\begin{enumerate}
  \item \textbf{(Bass 5.7)} Because $f$ is differentiable, $f$ is continuous. Since the Borel  $\sigma$-algebra contains all the open sets, then by Bass Proposition 5.6, $f$ is measurable.
Now, let \[
f_n = \frac{f(x+\frac{1}{n}) - f(x)}{\frac{1}{n}}
.\]
We can then express the derivative $f'$ as the limit of $f_n$:
\[
f' = \lim_{n \to \infty} f_n
.\] 
in which case the limits inferior and superior of $f_n$ are equal to each other (and the limit itself). Then, by Bass Proposition 5.7, each $f_n$ is measurable, and by Proposition 5.8, $f'$ is measurable.
  \item \textbf{(Bass 6.3)} We first take linearity of simple (non-negative) function's integrals as true from the first step of the proof of Theorem 7.4, and prove that simple functions obey the proposed equality. For any simple function $s$ and disjoint measurable sets $A_1, A_2$, we have that 
\[
  \int_{A_1} s + \int_{A_2}s = \sum_{n=1}^{m} a_n \mu(E_n \cap A_1) + \sum_{n=1}^{m} a_n \mu(E_n \cap A_2)
,\] 
where the coefficients $a_n$ and sets $E_n$ are those defined in the construction of a simple function. We then have by basic set logic and additivity of measures that, since $A_1$ and $A_2$ are disjoint, that the latter expression is equal to
\[
  \sum_{n=1}^{m} a_n \mu(E_n \cap (A_1 \cup A_2)) = \int_{A_1 \cup A_2} s
.\] 
With this equality, we prove the first of the two equalities in question.
\newline \indent If $s$ is a simple non-negative function and $s \le f$, we have that

 \[
   \int_{A_1 \cup A_2} s = \int_{A_1}s + \int_{A_2}s \leq \int_{A_1}f + \int_{A_2}f
.\] 
Since $\int_{A_1 \cup A_2} f = \sup\left\{\int_{A_1 \cup A_2} s| s \le f \right\}$, then
 \[
   \int_{A_1 \cup A_2} f \le \int_{A_1}f + \int_{A_2}f
.\]
We make a similar argument to prove inequality in the other direction. Let $s_1 \leq f$ on $A_1$, and zero elsewhere. Define $s_2$ the same on $A_2$. Then we have
\[
  \int_{A_1 \cup A_2}f \ge \int_{A_1 \cup A_2} s_1+s_2 = \int_{A_1}s_1 + \int_{A_2} s_2
,\]
where we are invoking our established linearity. With the integrals of $f$ defined over each of $A_1$ and $A_2$ each defined as the supremum of the integrals of the sets of functions $s_1$ and $s_2$, respectively, we get
\[
  \int_{A_1 \cup A_2}f \ge \int_{A_1}f + \int_{A_2}f
,\] 
satisfying equality. For the case where $f$ is integrable, consider the component functions $f^+$ and $f^-$, and apply the non-negative case to each of those functions.
\pagebreak
  \item \textbf{(Additional Problem \#1)} (We neglect the infinite-value cases in this proof) In the $\le $ case, we first note that $f-g$ is measurable by Proposition 5.7 and consider the equivalent difference sets. Then, the set $$\left\{ x \in X | f(x) - g(x) \le 0 \right\}$$ is measurable by the equivalent definitions of a measurable function in Proposition 5.5. Since the collection of measurable sets is a $\sigma$-algebra, and the set $$\left\{ x \in X | f(x) - g(x    ) \ge 0 \right\}$$ is also measurable, then the intersection of the $\le $ and $\ge $ sets, which is equal to
 $$\left\{ x \in X | f(x) - g(X) = 0 \right\},  $$
 is also measurable by the closure of $\sigma$-algebras under finite intersections.
\end{enumerate}

\end{document}
